Paper notes

### 2019-08-06 paper_notes.Rmd
implement in the abm

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.lp="fig:")

@@

# v_w <- 1 - e_w

@@

@@

@@

```{r ethnic_utility, moore neighborhood}

@@

@@

#  f_dist <- (o,ot,M,i,S)

@@

plot(value_mean_neighborhood,Utility_V, xlab = "Mean ethnic weight neighborhood j", ylab = "Value Utility",  main = "Value Utility for neighborhood j of agent i",  sub = name_V)

@@

\newcommand{\rocco}[1]{\textcolor{red}{{Rocco:}#1}} <!-- <- this is a command to appear in pdf -->
<!-- command not to appear in pdf -->

@@

e_w <- 0
v_w <- 0

>>>>

\newcommand{\rocco}[1]{\textcolor{red}{{Rocco:}#1}} <!-- <- this is a command to appear in pdf -->
<!-- command not to appear in pdf -->
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.lp="fig:")

@@

# Here functions that are used.

# Calculation ethnic utility (for each option)

@@

# Calculation value utility (for each option)

@@

# Probability (random utility with logistic regression) to relocate

@@

Write down how the three types of functions (Zhang, Schelling, new -> symmetric, threshold, costant) can be built out of the parameters M and S. Make a graph

Ethnic utility, separating ethnic_weight and ideal payoff for ethnicity (i_e) -> based on ethnicity of agents (color)
The ethnic weight follows the beta distribution, *maybe* report Blitzstein 4 beta cases, and anyway considering ethnic_weight and value_weight are complementary

```{r ethnic_utility, moore neighborhood, include=TRUE, echo=FALSE}

@@

Value utility, based on agents' desired distance (i_v) between the agent's ethnic_weight (e_w) and neighborhood's average ethnic_weight (calculated out of agents residing there)
Calculate ethnic weight average of neighborhoods with n agents > 0.

 **check:** Explain how S and M vary for the constant function, the comment seems lost

@@

@@

plot(value_mean_neighborhood,Utility_V, xlab = "Mean ethnic weight neighborhood j", ylab = "Value Utility neighborhood j",  main = "Value Utility for neighborhood j of agent i",  sub = name_V)

@@

Once calculated the ethnic utility and value utility, apply prob above (logistic function) in the decision rule of the agent, with prob(to_new) >= random-float 0-1

@@

e_w <- 0.8
v_w <- 1 - e_w
